gmin figures

### 2017-08-16 figures.Rmd
Some references added; bug fix in load
Added crop genotypes figure

```{r, fig.width=6, fig.height=5}
gmin_by_family(gmindat)
```

```{r, fig.width=6, fig.height=5}
gmin_by_order(gmindat)
```

>>>>

```{r, fig.width=6, fig.height=5, warning=FALSE}
gmin_by_family(gmindat)
```

```{r, fig.width=6, fig.height=5, warning=FALSE}
gmin_by_order(gmindat)
```

```{r, fig.width=6, fig.height=5, warning=FALSE}
figure_crop_genotypes(cropgmin)
```
